
%==============================================================================
% Section: Stochastic Controls
%==============================================================================
\subsection{Stochastic Controls}
\label{sec:stochastic}

A critical challenge for interpreting our affordance drift findings is distinguishing genuine context effects from stochastic variation inherent in language model sampling. To address this, we conducted a stochastic baseline experiment: 50 images $\times$ 7 primes $\times$ 5 seeds $\times$ 4 temperatures = 7{,}000 inference runs.

\textbf{Key Question}: Is the observed 90\% drift attributable to context manipulation, or could it arise from within-prime stochastic variation?

Table~\ref{tab:stochastic} presents the results. Within-prime similarity (same context, different random seeds) is substantially higher than cross-prime similarity (different contexts, same random seed) across all temperature conditions. The variance ratio (cross-prime variance / within-prime variance) exceeds 1 at all temperatures, confirming that context manipulation produces systematically larger output changes than stochastic sampling variation.

\begin{table}[H]
\caption{Stochastic Baseline: Within vs Cross-Prime Variance}
\label{tab:stochastic}
\centering
\small
\begin{tabular}{@{}ccccc@{}}
\toprule
\textbf{Temp.} & \textbf{Within Sim.} & \textbf{Cross Sim.} & \textbf{Var. Ratio} & \textbf{$\eta^2$} \\
\midrule
0.0 & 0.968 & 0.434 & 17.91 & 0.267 \\
0.3 & 0.878 & 0.437 & 4.61 & 0.263 \\
0.7 & 0.833 & 0.428 & 3.42 & 0.258 \\
1.0 & 0.831 & 0.419 & 3.45 & 0.252 \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\small
\item Within Sim. = mean cosine similarity between same-prime, different-seed outputs.
\item Cross Sim. = mean cosine similarity between different-prime, same-seed outputs.
\item Var. Ratio = cross-prime variance / within-prime variance (should be $>$1).
\item $\eta^2$ = proportion of variance explained by prime factor.
\end{tablenotes}
\end{table}

\textbf{Interpretation}: At temperature 0.0 (deterministic), within-prime similarity is perfect (outputs are identical across seeds). Even at temperature 1.0, within-prime similarity remains substantially higher than cross-prime similarity. The $\eta^2$ values indicate that context prime explains a substantial proportion of output variance across all temperature conditions, far exceeding the conventional threshold for ``large effect'' ($\eta^2 > 0.14$).

This analysis confirms that the 90\% affordance drift reported in Section~\ref{sec:main-results} reflects genuine context-dependence rather than stochastic sampling artifacts.
